\documentclass[12pt, titlepage]{article}
\usepackage{hyperref}

\title{Feedback Controls Lab Weekly Report \\ \normalsize{Week 2}}
\author{Aydan Vissing, Brady Schick, Gabriel Southwell, Simon Ross}
\date{\today}

\begin{document}
\maketitle

\section*{Aydan Vissing - CFO (13 hrs spent)}

I spent time this week getting the rig ready to 3D print and once that was done, I spent the rest of my time getting QT designer set up and begun the creation of the GUI. I spent a lot of time reading through MatPlotLib's documentation and trying to learn how the functions work. The goal this week is to research numpy and scipy as well as get some data to work with from Gabe to plot with both and get it to work in the GUI. 

\section*{Brady Schick - CTO (12 hrs spent)}

This week mainly involved figuring out how to code and tune xy position control, as well as discussion on other problematic parts of the simulation.

\section*{Gabriel Southwell - CSO (12.5 hrs spent)}

This week I worked on delegating some of the programming tasks. I am exploring different options like Jira for organizing the tasks and keeping information about them in one place. Not sure what I will go with yet. 

Simon and I were able to test the motor control driver I had written earlier and it works great. We were able to spin all the motors at various speeds.

I put a ton of work into understanding the Crazyflie flight controller and how it was adapted to work on the ESP-Drone. The cf project is huge and has a lot of features we don't need so it has been a lot to sort through all of it. I spent a ton of time going through and replacing hardware calls with equivalent calls to our hardware. I am optimistic about making it work though. 

\section*{Simon Ross - CEO (12 hrs spent)}

This week was far more productive for me than the previous one---I even managed to make some real progress (wink). More importantly, however, the team has been making an excellent effort on getting the drone into the air. We've all been working our tails off for this project, and I think that's great.

I started the week by learning a bit more about the programming structure of the project. We had our team meeting and then I immediately started assembling the board for a working prototype. On Tuesday, I soldered on a replacement power regulator which works spectacularly. Then on Thursday, I put the rest of the drone together and tested the motors with Gabe. His driver worked successfully, and all of the motors turned---perhaps a little too well. One of the propellers got destroyed in the process and I had a bit more soldering to do. At least it made the first test exciting. Finally, I made a few tweaks to our logo for the app UI. Friday and Saturday were spent on learning more about coding for the ESP and working on a simple battery checker circuit to take something off Gabe's hands.

This upcoming week, I'm going to lean harder into the coding process, hopefully finishing off the battery checker and moving on to more important tasks. I'll also need to do a little more soldering as our battery is too strong for the ADC unit in its current configuration. We'll fix this problem in board v2, but thankfully these small changes aren't hindering testing progress. Gabe has been making great headway on the controller code, Aydan almost has a testing rig ready, and Brady's controller work is incredible. I'm looking forward to what this next week will bring.

\end{document}