\documentclass[12pt, titlepage]{article}
\usepackage{hyperref}

\title{Feedback Controls Lab Weekly Report \\ \normalsize{Week 8}}
\author{Aydan Vissing, Brady Schick, Gabriel Southwell, Simon Ross}
\date{\today}

\begin{document}
\maketitle

\section*{Aydan Vissing - CFO (14 hrs spent)}

I spent the week getting the GUI ready for the milestone and looking for new props for the drone. I spent a bit of time over break asking chatgpt questions about how to actually continue to make the GUI do more of the things we want it to do and I plan on attempting to implement them this week. 

\section*{Brady Schick - CTO (14 hrs spent)}

Most of the work was done during spring break. Since I didn't have the drone with me to tune, I worked on moving the MATLAB simulation over to Python. It works almost to the functionality that it was working in MATLAB, except I currently don't have a way to toggle the animation on and off.

Now that I'm back on campus, most of my time will probably be spent working on tuning the actual drone.

\section*{Gabriel Southwell - CSO (3 hrs spent)}

This week I was unable to get much done due to it being a busy week and having two interviews that I had to prep for. I also was unable to work any on break since I was on a GO trip.

I started working on making the cflib scripts dump to csv. 

\section*{Simon Ross - CEO (12 hrs spent)}

This week and last I worked on the drone scripting process, and will likely polish off the file transfer this upcoming week. By the milestone, the drone was able to receive a script file from the computer sent over serial and return the contents of this file once it was saved. Over break, I increased the reliability of this process, and have almost gotten it to 100\%. Additionally, I will probably lean into Python app development over this coming week (to help Aydan out) and see what Gabe and Brady need, filtering their work into my continued scripting progress.

\end{document}