\documentclass[12pt, titlepage]{article}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=magenta]{hyperref}

\title{Feedback Controls Lab Weekly Report \\ \normalsize{Week 12}}
\author{Aydan Vissing, Brady Schick, Gabriel Southwell, Simon Ross}
\date{\today}

\begin{document}
\maketitle

\section*{Aydan Vissing (10 hours spent)}

Spent some time in meetings and remodeling the frame, testing the new structure of the motor mounts and prop guards. I found the new structure to be a lot better than the previous one, less prone to breaking. I spent a lot of time on the last mini-project and then continued to do more design on the frame. I am waiting now on the PCB to be complete before I can finish frame design. 

\section*{Brady Schick (8 hours spent)}

The time for this week was split between continuing work on the MATLAB simulation and on Mini-Project 4.

\section*{Gabriel Southwell (12 hours spent)}

This week I did the the Serial Communication Mini-Project. I got Dr. Fredette's permission to use what I already have done on the MPU 6050 with the ESP32 for the second part of the project. This let me spend more time on the project.

This week I made some pretty good progress on the problems that I had been stuck on. After looking at the documentation for both the vl53l and the MPU6050, I determined that the vl53 would be harder to re-implement if I had to. 

This changed my approach to getting the vl53ls to work properly and then trying to add the MPU back in. I decided on this https://github.com/TeschRenan/ESP32-VL53L1X.git vl53l library because it seems easy to use and includes functions for re-addressing the sensors. I was able to get one sensor to read data, but I did not have time to finish writing and testing the readdressing function. 

As for adding the MPU back in, I an not sure what approach I want to take for it. There are three options for what I could do:

\begin{itemize}
\item Writing a wrapper for an existing MPU library that translates the i2c calls into the equivalent calls for the library the vl53l uses
   \begin{itemize}
   \item	This would work and not be too hard, but it could come with some performance impacts. 
   \end{itemize}
\item Taking an existing library and patching it to use the same library as the vl53l
   \begin{itemize}
   \item This would be a little harder and it might not be possible for most libraries. But it would be native performance
   \end{itemize}
\item Writing my own MPU library
   \begin{itemize}
   \item I have looked at all the functions I would need to implement, and my hubris says it would be easy :) 
   \end{itemize}
\end{itemize}

I will look into these options after I get the vl53l re-addressing working. 

\section*{Simon Ross (26.5 hours spent)}

I worked on the controls mini-project and the PCB design this week. Because of the ongoing PCB work, I again don't have enough time to write a drawn-out report. Ultimately, I think the team is making great progress and that our main pinch point is the PCB right now. I'll try to finish it by Friday.

The prototype (now PCB) is the main thing on the schedule as well, with an interface prototype being the runner up. I'll make sure to discuss this soon.

\end{document}