\documentclass[12pt, titlepage]{article}
\usepackage{hyperref}

\title{Feedback Controls Lab Weekly Report \\ \normalsize{Week 3}}
\author{Aydan Vissing, Brady Schick, Gabriel Southwell, Simon Ross}
\date{\today}

\begin{document}
\maketitle

\section*{Aydan Vissing - CFO (12 hrs spent)}

I have been continuing to build the desktop application, which has proven to be a lot of research that I didn't expect. Trying to integrate the GUI with file I/O and Matplotlib is more complex than I anticipated but it seems to be moving along and I anticipate having at least one of the plots working by the end of this week, hopefully. 

\section*{Brady Schick - CTO (6 hrs spent)}

This week was not the most productive. I implemented coordinate conversions in the xy controls and implemented a basic integration windup pervention and re-tuned the controller as needed so that good elevation control worked for up to 3 meters. The rest of the time was spent trying to figure out the current robustness of the controller.

\section*{Gabriel Southwell - CSO (12 hrs spent)}

This week I continued to work on adapting the flight controller to work for our system. The Espressif team already did a lot of good work making the Crazyflie firmware work and compile on esp-32s, but adapting for us is still a lot. Much of what I have been doing is slowly following the control flow of the firmware and snipping the features that we are not going to use.

\section*{Simon Ross - CEO (10 hrs spent)}

This week I spent a lot of time getting to know the codebase - learning how the objects are structured and the basic ESP-IDF functionality. It's been different than what I've worked with before, but I'm picking it up quickly---got a battery checking script done this week and I'll be able to check it early next week. 

Additionally, I spent some time making a wiring harness for the drone so that we can run it using the lab power sources. This way we don't have to spend so much time charging and monitoring batteries.

\end{document}